---
title: "Practice_2_GitHub"
author: "Batoule Hyjazie"
date: "26/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
#Configuring __GitHub__ in RStudio 
=======
#Configuring __GitHub__ in RStudio
>>>>>>> 1236c7ac26ff39f1f0a5739905f48899647f35c9

##Check Configure Git
usethis::git_sitrep()

##Configure Git Accountt
usethis::use_git_config(
  use.name="BatouleHyjazie",
  user.email="bhyja038@uottawa.ca"
)

##Check Again
usethis::git_sitrep()

##Create a PAT
usethis::create_github_token()
credentials::set_github_pat()

##Check Again
usethis::git_sitrep()

##Initialize Project for Git
usethis::use_git()

##To Create GitHub Repo and Link It
credentials::set_github_pat()
usethis::use_github()
usethis::git_vaccinate()

##Terminal
git branch -M main
git push -u origin main

##Data
```{r penguins, echo=FALSE}
library(palmerpenguins)
data(package = 'palmerpenguins')
plot(penguins$flipper_length_mm, penguins$body_mass_g, 
xlab="Flipper Length (mm)", ylab="Body Mass (g)", main="Body Mass vs Flipper Length")
```
